### 2020-04-28 serial.tex
undefined macro

In order to define forward and backward serial interval distributions, we begin by writing the total number of serial intervals \bmb{explain more please \ldots} between time $\pi$ (when the infector developed symptoms) and $\delta$ (when the infectee developed symptoms), which can be expressed as an integral over all of the possibilities for the infection times of the infector $\alpha_1$ and the infectee $\alpha_2$:
\begin{equation}
T(\pi,\delta) = \int_{-\infty}^{\pi} \int_{\alpha_1}^{\delta} \Rc (\alpha_1) i(\alpha_1) h_{\alpha_1}(\pi-\alpha_1, \alpha_2 - \alpha_1) k_{\alpha_2}(\delta - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1,
\end{equation}
where $\Rc(\alpha_1)$ is the case reproduction number (i.e., the average number of secondary cases caused by a primary case infected at time $\alpha_1$, \cite{fraser2007estimating}) \bmb{is \Rc the same as ``forward \R measured at a particular time''?}, $i(\alpha_1)$ is incidence, $h_{\alpha_1}(\pi-\alpha_1, \alpha_2 - \alpha_1)$ is the joint probability distribution describing the forward incubation period $\pi-\alpha_1$ and forward generation interval $\alpha_2 - \alpha_1$ of an individual infected at time $\alpha_1$ (in this case, the infector), and $k_{\alpha_2}(\delta-\alpha_2)$ describes the marginal probability distribution of $h_{\alpha_2}$ describing the forward incubation period $\delta-\alpha_2$ of an individual infected at time $\alpha_2$ (in this case, the infectee). 
Then, the forward serial-interval distribution is proportional to $T(\pi, \pi+\tau)$. Substituting $x=\pi-\alpha_1$ and $\sigma=\alpha_2-\alpha_1$, we have:
\begin{equation}
f_\pi(\tau) \propto \int_{0}^{\infty} \int_{0}^{\max(0,x+\tau)} \Rc (\pi-x) i(\pi-x) h_{\pi-x}(x, \sigma) k_{\pi-x+\sigma}(x-\sigma+\tau) \dsigma \dx
\end{equation}
Likewise, the backward serial-interval distribution is proportional to $T(\delta-\tau, \delta)$. 
This time, we substitute $x=\delta-\alpha_2$ and $\sigma=\alpha_2-\alpha_1$ to get:
\begin{equation}
b_\delta(\tau) \propto \int_{0}^{\infty} \int_{\max(0, \tau-x)}^{\infty} \Rc (\delta-x-\sigma) i(\delta-x-\sigma) h_{\delta-x-\sigma}(x+\sigma-\tau, \sigma) k_{\delta-x}(x) \dsigma \dx.
\end{equation}

>>>>

In order to define forward and backward serial interval distributions, we begin by writing the total number of serial intervals \bmb{explain more please \ldots} between time $\pi$ (when the infector developed symptoms) and $\delta$ (when the infectee developed symptoms), which can be expressed as an integral over all of the possibilities for the infection times of the infector $\alpha_1$ and the infectee $\alpha_2$:
\begin{equation}
T(\pi,\delta) = \int_{-\infty}^{\pi} \int_{\alpha_1}^{\delta} \Rc (\alpha_1) i(\alpha_1) h_{\alpha_1}(\pi-\alpha_1, \alpha_2 - \alpha_1) k_{\alpha_2}(\delta - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1,
\end{equation}
where $\Rc(\alpha_1)$ is the case reproduction number (i.e., the average number of secondary cases caused by a primary case infected at time $\alpha_1$, \cite{fraser2007estimating}) \bmb{is \Rc the same as ``forward \Rx measured at a particular time''?}, $i(\alpha_1)$ is incidence, $h_{\alpha_1}(\pi-\alpha_1, \alpha_2 - \alpha_1)$ is the joint probability distribution describing the forward incubation period $\pi-\alpha_1$ and forward generation interval $\alpha_2 - \alpha_1$ of an individual infected at time $\alpha_1$ (in this case, the infector), and $k_{\alpha_2}(\delta-\alpha_2)$ describes the marginal probability distribution of $h_{\alpha_2}$ describing the forward incubation period $\delta-\alpha_2$ of an individual infected at time $\alpha_2$ (in this case, the infectee). 
Then, the forward serial-interval distribution is proportional to $T(\pi, \pi+\tau)$. Substituting $x=\pi-\alpha_1$ and $\sigma=\alpha_2-\alpha_1$, we have:
\begin{equation}
f_\pi(\tau) \propto \int_{0}^{\infty} \int_{0}^{\max(0,x+\tau)} \Rc (\pi-x) i(\pi-x) h_{\pi-x}(x, \sigma) k_{\pi-x+\sigma}(x-\sigma+\tau) \dsigma \dx
\end{equation}
Likewise, the backward serial-interval distribution is proportional to $T(\delta-\tau, \delta)$. 
This time, we substitute $x=\delta-\alpha_2$ and $\sigma=\alpha_2-\alpha_1$ to get:
\begin{equation}
b_\delta(\tau) \propto \int_{0}^{\infty} \int_{\max(0, \tau-x)}^{\infty} \Rc (\delta-x-\sigma) i(\delta-x-\sigma) h_{\delta-x-\sigma}(x+\sigma-\tau, \sigma) k_{\delta-x}(x) \dsigma \dx.
\end{equation}
